Interoception Scale - Data Cleaning

### 2024-12-04 study1/analysis/1_cleaning.qmd
Done Education, Ethnicity, Disciple ToDos

p_eth <- df |> 
  mutate(Ethnicity = case_when(
    Ethnicity == "central Asia" ~ "Central Asian",
    Ethnicity == "American of African descent, Native American and European" ~ "Mixed",
    Ethnicity == "southern european" ~ "White",
    Ethnicity == "persian" ~ "Middle Eastern/North African",
    Ethnicity %in% c("Berber","Native American","Turkish","turkish") ~ "Other",
    TRUE ~ Ethnicity, 
    )) |>
  filter(!is.na(Ethnicity)) |> 
  ggplot(aes(x = "", fill = Ethnicity)) +
  geom_bar() +
  coord_polar("y") +
  theme_minimal() +
  theme(
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    axis.text.y = element_blank(),
    axis.title.y = element_blank()
  )

>>>>

p_eth <- df |>
  filter(!is.na(Ethnicity)) |> 
  ggplot(aes(x = "", fill = Ethnicity)) +
  geom_bar() +
  coord_polar("y") +
  theme_minimal() +
  theme(
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    axis.text.y = element_blank(),
    axis.title.y = element_blank()
  )
